Stat 400 Presentation

### 2021-12-08 Stat 400 presentation.Rmd
Intro slides (mostly complete)

>>>>

## Novel approach for Monte Carlo simulation of the new COVID-19 spread dynamics

Original Authors: Stavros Maltezos, Angelika Georgapakopoulou

Resimulated by: Nathan Hemenway, Mark Hinds, Ian Hall

## Introduction

- Aim to investigate the transmission and incubation random processes of COVID-19.

- Our focus will be on simulating daily infection case counts.

- The goal of the study is to generate epidemiological based on natural mechanism of transmission of this disease assuming random interactions of a large-finite number of individuals in very short distance ranges.

## Assumptions

- The transmission of the virus occurs when the physical distance between individuals decreases to where the probability of transmission converges to one, asymptotmically.

- the step of movement of people is a randomly assigned process.

- the specific parameters of focus will be recovery and incubation time.

##

## General Model

- Step Function
    - Consider dots on a plane, with random

- This is approached through an SIR model: Susceptible, Infected, Recovered. All change based on time.

## Variables

- not complete
